Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Minor revision.

\textbf{We show here how a multiple constraints solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector function that contains the concatenation of all constraints
  defining $\manifold$. Note that as the intersection of two or more
  manifolds is also a manifold, this multi-constraint solver allows us
  also to generate configurations that lie at the intersection of
  several manifolds.}

@@

The algorithm that animates a statically balanced path into a
dynamically balanced walk trajectory has been inspired by the previous
small-space controllability proof. \textbf{Given a statically balanced
  path $p$ verifying the cart-table model approximation constraints,
  we start by placing footprints corresponding to the nominal walk
  pattern of the robot. Given the footprints, we compute a ZMP
  trajectory, derive foot trajectories, and a preview controller
  outputs a corresponding CoM trajectory. Classic numerical
  Jacobian-based prioritized inverse kinematics methods prove to be
  very useful to generate a dynamic walking trajectory while trying to
  accomplish secondary tasks, such as following a reference
  configuration trajectory. We use the same framework which was
  developped in \cite{yoshida2006tds}.}

>>>>

\textbf{We show here how a multiple constraints solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector function that contains the concatenation of all constraints
  defining $\manifold$. Note that as the intersection of two or more
  manifolds is also a manifold, this constraint solver allows us also
  to generate configurations that lie at the intersection of several
  manifolds.}

@@

The algorithm that animates a statically balanced path into a
dynamically balanced walk trajectory has been inspired by the previous
small-space controllability proof. \textbf{Given a statically balanced
  path $p$ verifying the cart-table model approximation constraints,
  we start by placing footprints corresponding to the nominal walk
  pattern of the robot. Given the footprints, we compute a ZMP
  trajectory, derive foot trajectories, and a preview controller
  outputs a corresponding CoM trajectory. Classic numerical
  Jacobian-based prioritized inverse kinematics methods prove to be
  very useful to generate a dynamic walking trajectory while trying to
  accomplish secondary tasks, such as following a reference
  configuration trajectory. We use the same framework which was
  developed in \cite{yoshida2006tds}.}
